Poker Chips, Earthquakes, and Computation

### 2014-09-26 draft0.tex
edited section 3.0

\begin{definition} 
We say that a board is finite if the total number of chips on it is finite. That is a board $f$ is finite if the sum
\begin{equation}
S= \sum_{(x,y) \in \mathbb{Z} \times \mathbb{Z}} f(x,y) 
\end{equation}
is finite. 
We denote the set of finite boards as $\mathcal{B}_f$.
\end{definition}

@@

In this section we show that any board with a finite number of chips on it will reach a stable state after applying finitely many local or global earthquakes. 
We do so by showing first that if a local or global earthquake changes the state of a board then no sequence of local or global earthquakes can transform the output board back into the original board. 
We will then show that for a given finite board there is a maximum number of states that local or global earthquakes can transform it into. 
Together these show that all finite boards eventually become stable. 
\begin{theorem}
\label{finitestability}
If the initial board has a finite number of chips, there exists an $N$ such that after $N$ global earthquakes or $N$ local earthquakes the resultant board will be stable.
\end{theorem}

>>>>

\begin{definition} 
We say that a board is finite if the total number of chips on it is finite. That is a board $f$ is finite if the sum
\begin{equation}
S= \sum_{(x,y) \in \mathbb{Z} \times \mathbb{Z}} f(x,y) 
\end{equation}
is finite. 
We denote the set of finite boards as $\mathcal{B}_F$.
\end{definition}

@@

In this section we show that any finite board will reach a stable state after finitely many local or global earthquakes. 
We do so by showing that if a local or global earthquake changes the state of a board then no sequence of local or global earthquakes can transform the output board back into the original board. 
We will then bound the maximum number of configurations that local or global earthquakes can transform it into. 
Together these show that all finite boards stabilize. 
\begin{theorem}
\label{finitestability}
If $f \in B_F$, there exists $N, M > 0$ such that after $N$ global earthquakes or $M$ local earthquakes the resultant board will be stable, or for all $m > 0$, $GE^{N+m}(f) = GE^N(f)$, and $LE^{M+m}(f, X_1 \cup X_2) = LE^M(f, X_1)$.
\end{theorem}
